Clouds and Radiation in a mock-Walker Circulation

### 2019-10-14 Silvers_WalkerCell.tex

\begin{figure}
  \centering
      \includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
          \caption{Domain mean total condensate (liquid + ice).  Solid lines show experiments with LWCRE on
          and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
          convection except the thin yellow lines which have the convective parameterization turned on.}
  \label{fig:TotCond}
\end{figure}

@@

We can see clearly that the interactions between longwave radiation and clouds act to dry the troposphere in the regions of subsidence 
more than the cases when the longwave CRE is not active.  This is especially true for the simulations with a grid-spacing of 1 km 
and 2 km.  While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, 
there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the LW CRE on, significant 
low-level clouds are formed, leading to a radiative cooling of almost 10K/day, and a radiative cooling of around -7K/day.   However, 
when the LW CRE is off, there is no appreciable difference in the low-level diabatic profiles among the models with 3 grid-spacings.   It 
is also clearly seen that the LW CRE decreases the upper-level ice-condensate for models of all grid-spacings while dramatically 
increasing the low-level liquid condensate.

When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.

Relative to simulations with a grid-spacing of $25 \textit{km}$, the simulations with explicit convection can be characterized as having: 
\begin{itemize}
  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered over the maximum of SST.  
  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models can have a relative humidity 
  that is 40\% higher than in the parameterized, lower resolution simulations.  
  \item two to four times more ice condensate above about 600 hPa but only about half as much liquid condensate below about 700 hPa.
  \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 
  simulations are 10-20\% higher (3.5-3.9 mm/d).  
  \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
  %\item much less vertical shear.  
\end{itemize}

>>>>

\begin{figure}
  \centering
      \includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
          \caption{Domain mean total condensate (liquid + ice) for P25 (thin yellow), E25 (yellow), 
          E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on
          and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
          convection except the thin yellow lines which have the convective parameterization turned on.}
  \label{fig:TotCond}
\end{figure}

@@

We can see clearly that the interactions between longwave radiation and clouds act to dry the troposphere in the regions of subsidence 
more than the cases when the longwave CRE is not active.  This is especially true for the simulations with a grid-spacing of 1 km 
and 2 km.  While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, 
there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the 
LW CRE on, significant low-level clouds are formed, leading to a radiative cooling of almost 10K/day, 
and a radiative cooling of around -7K/day.   However, when the LW CRE is off, there is no appreciable 
difference in the low-level diabatic profiles among the E25, E2, and E1 experiments.   It 
is also clearly seen that the LW CRE decreases the upper-level ice-condensate for E25, E2, and E1 
experiments but dramatically increases the low-level liquid condensate for E25 and P25 (Figure 
\ref{fig:TotCond}).

When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar 
distribution and magnitude of surface enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the 
LW CRE is on, there are differences between the resolutions that can be as large as $80 \, \rm{W/
m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are 
confined to the regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.

Relative to simulations with a grid-spacing of $25 \textit{km}$, the E2 and E1 experiments can be characterized as having: 
\begin{itemize}
  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered over the maximum of SST.  
  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models can have a relative humidity 
  that is 40\% higher than in the parameterized, lower resolution simulations.  
  \item two to four times more ice condensate above 600 hPa but only about half as much liquid condensate below 700 hPa.
  \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 
  simulations are 10-20\% higher (3.5-3.9 mm/d).  
  \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
  %\item much less vertical shear.  
\end{itemize}
